\subsection{Future Work}
Take note of current testbed contain limitation. It accommodates basic regulation of a operating radio device, however, a set of much detailed and rigorous rules much be integrated to the system for commercial or military uses. The testbed is built around some CR algorithm proposal under field of reactive channel selection. Area such as proactive channel selection requires another platform to keep all the spectrum data for regional network to access. This requires a setup of a centralize data division designate to process spectrum history. With proactive channel selection system, the focus will be minimizing the channel switching delay of the hardware. Speaking of sharing knowledge to from a region to another, simply adding more BSs can accomplish some of that. This take it to the next level of cognitive radio network, which allow any fresh CR project launch adopt to the system very easily. Another aspect of the study, geo-barrier during employment, is also very important. Each device would not only be capable of recognizing other device, they must also need to analysis the signal strength and advise the user for a better location. That is where city planning or location management come into place. Looking back to the hardware, in fact, all should take this thesis project as purely an sample of the system. The end goal for this system is to fully integrate at a printed circuit board. These could be continually worked on and refined in the near future. 

\subsection{Summary}
In conclusion, this project integrates selective standards and guidelines that are given to form a CRN into a scalable testbed for future studies. The information gather is initially around CR technology itself. To establish a network, it involves some basic protocol and radio frequency knowledge. Making a physical testbed, it is necessary to go through the whole hardware development and verification process. The experiment run in the testbed results realistic emulated data, which reflects the performance of certain CR logic. 

Now that with the understanding of the direction of CRN would go toward, all should stay tuned to this technology. Soon it may be implementing in our local network before you realizing it.
